---
title: "Data Tidying FY20 Search 1 Email"
author: "Office of Marketing and Brand Management"
date: "8/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(tidyverse)
library(stringr)
library(kableExtra)
```

```{r}
Overall_1 <- read.csv("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Campaign (1).csv", header = T, stringsAsFactors = F)
Overall_2 <- read.csv("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Campaign (2).csv", header = T, stringsAsFactors = F)
Overall <- rbind.data.frame(Overall_1, Overall_2)
Overall <- Overall %>% na.omit()
Overall[12,2] <- "FA20 Search 1J20 â\200” Email 03"
#fix name

Overall$Name <-  gsub('â\200”','',Overall$Name)
```


```{r}
kable(Overall)
# Overall$Name <- factor(Overall$Name, levels = c("FA20 Search 1S20 Email 01", 
#                                                 "FA20 Search 1S20 Email 02",
#                                                 "FA20 Search 1S20 Email 03",
#                                                 "FA20 Search 1S20 Email 04",
#                                                 "FA20 Search 1S20 Email 05",
#                                                 "FA20 Search 1S20 Email 06",
#                                                 "FA20 Search 1S20 Email 07",
#                                                 "FA20 Search 1J21 Email 01", 
#                                                 "FA20 Search 1J21 Email 02", 
#                                                 "FA20 Search 1J21 Email 03",
#                                                 "FA20 Search 1J21 Email 04",
#                                                 "FA20 Search 1J21 Email 05",
#                                                 "FA20 Search 1J21 Email 06",
#                                                 "FA20 Search 1J21 Email 07"))
# 
# Overall$Name <- as.character(Overall$Name)

Overall <- Overall%>% 
  mutate(Date.Time.Sent = as.POSIXct(Date.Time.Sent, format = "%m/%d/%Y %I:%M %p")) %>% 
  separate(Date.Time.Sent, into = c("Date", "Time"), sep = " ") %>% 
  separate(Name, into = c("Campaign", "Email"), sep = " (?=[^ ]+$)")%>% 
  mutate(Campaign = substring(Campaign, 6),
         Sent = Emails.Sent, 
         Open.Rate = round(Open.Rate, 2), 
         Deliverability.Rate = round(Deliverability.Rate,2),
         Unique.Click.Through.Rate = round(Unique.Click.Through.Rate, 2)) %>% 
  select(Job.ID, Campaign, Email, Date, Sent, Open.Rate, Deliverability.Rate, Unique.Click.Through.Rate)

Overall
kable(Overall %>% select(Campaign, Email, Open.Rate, Unique.Click.Through.Rate)) %>% 
  kable_styling()


kable(Overall, caption = "Search Performance by Campaign and Email") %>%
  kable_paper("striped", full_width = F) %>%
  pack_rows("Senior Search", 1, 8) %>%
  pack_rows("Junior Search", 8, 14)     
```



2.


Tidy links data

```{r}
#load excel reader libraries
library(devtools)
# install.packages("devtools")
#devtools::install_github("tidyverse/readxl")
library(readxl)
FA20_Search_1S20_Email_07 <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_890526_Overview_08282020.xls", skip = 12
                                        , col_names = c("Event", "Unique", "Total", "Percentage"))
# na = 0
FA20_Search_1S20_Email_07 <- FA20_Search_1S20_Email_07 %>% mutate_at(vars("Unique", "Total", "Percentage"), as.numeric)


 FA20_Search_1S20_Email_07 <- FA20_Search_1S20_Email_07 %>% replace(is.na(.), 0)
# mutate at Unique total percentage to numbric
```

```{r junior email 4}

`FA20 Search 1J21 — Email 04` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_810751_Link_08282020.xls", skip = 12, col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")) 

`FA20 Search 1J21 — Email 04` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 04`
```



```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832593_Link_08282020.xls

```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```





C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832593_Overview_08282020.xls



```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_877523_Link_08282020.xls

```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_877524_Link_08282020.xls
```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_877524_Overview_08282020.xls
```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_890524_Link_08282020.xls
```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_890526_Link_08282020.xls
```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_890526_Overview_08282020.xls

```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_742135_Link_08282020 (1).xls

```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_742135_Link_08282020.xls

```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_742135_Overview_08282020.xls
```{r }

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
``````{r junior email 5}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_742137_Link_08282020.xls

```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_761147_Link_08282020.xls

```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_761149_Link_08282020.xls

```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_761149_Overview_08282020.xls

```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_790439_Link_08282020.xls

```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_790439_Overview_08282020.xls

```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_790440_Link_08282020.xls

```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_810750_Link_08282020.xls

```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```


C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_810750_Overview_08282020.xls

```{r}

`FA20 Search 1J21 — Email 05` <- read_excel("C:/Users/christine.iyer/Box/FY21_Email/FY20_Search _1_Email_Performance/Raw Data/Job_832590_Link_08282020.xls"
                                            , 
                                            skip = 12, 
                                            col_names = c("Link Name", "Blank", "Unique Clicks", "% of Unique Clicks", "Total Clicks", "% of Total Clicks", "Net CTRs")
                                            ) 

`FA20 Search 1J21 — Email 05` <- `FA20 Search 1J21 — Email 04` %>% replace(is.na(.), 0)
`FA20 Search 1J21 — Email 05`
```

[Github ](https://github.com/edithbird/FY20_EmailPerformance-Search1)

[Wrike FY21 Search](https://www.wrike.com/open.htm?id=555743625)

[Tableau Viz](https://public.tableau.com/shared/94DD43C45?:display_count=y&:origin=viz_share_link)




